\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-18 canonicitymodel.tex
Adapt style guide.

We follow the reducibility argument from \citep{coquand2018canonicity,sterling2019algebraic, kaposi2019gluing} to construct the canonicity model. We will first specify the formulation of the most basic canonicity theorem.

@@

Canonicity is one of the basic criteria to consider a dependent type theory to be ``a programming language or as a computational foundation for mathematics''\footnote{See nlab explanation: \href{https://ncatlab.org/nlab/show/canonical+form}{Canonical Form}}.
We can even argue that, if this theorem is proven in a constructive meta-logic\footnote{QIIT does have computational content\citep{altkap2016}}, 
then by Curry-Howard Correspondence, this theorem provides a big-step interpreter for closed term of boolean type.

@@

Another helpful analogy of the canonicity model is that $"Tm"_p~\Gamma^C~"T"^C~"t"$ can be understood as $"t" \in \{$ Reducible Terms of type $T$ (and $T_p$) in context $\Gamma$ (and $\Gamma_p$) $\}$. The latter is more conventional and the former can be understood as type theoretic encoding of the latter\footnote{We usually use predicate to encode "belong to" relation in type theory}. From this perspective, this part of the canonicity model is quite similar to how conventional (proof-irrelevant) logical relation is carried out\citep{skorstengaard2019introduction} --
using the terminology of the conventional formulation, $\Gamma_p$ will be the set of substitution into closed reducible terms, and we will prove $t[\gamma] \in T_p$, a set of closed reducible term of type $T$ when $\gamma \in \Gamma_p$.

>>>>

We follow the reducibility argument from~\citet{coquand2018canonicity,sterling2019algebraic, kaposi2019gluing} to construct the canonicity model. We will first specify the formulation of the most basic canonicity theorem.

@@

Canonicity is one of the basic criteria to consider a dependent type theory to be ``a programming language or as a computational foundation for mathematics''.\footnote{See nlab explanation: \href{https://ncatlab.org/nlab/show/canonical+form}{Canonical Form}}
We can even argue that, if this theorem is proven in a constructive meta-logic\footnote{QIIT does have computational content~\cite{altkap2016}}, 
then by Curry-Howard Correspondence, this theorem provides a big-step interpreter for closed term of boolean type.

@@

Another helpful analogy of the canonicity model is that $"Tm"_p~\Gamma^C~"T"^C~"t"$ can be understood as $"t" \in \{$ Reducible Terms of type $T$ (and $T_p$) in context $\Gamma$ (and $\Gamma_p$) $\}$. The latter is more conventional and the former can be understood as type theoretic encoding of the latter\footnote{We usually use predicate to encode "belong to" relation in type theory}. From this perspective, this part of the canonicity model is quite similar to how conventional (proof-irrelevant) logical relation is carried out~\cite{skorstengaard2019introduction}---using the terminology of the conventional formulation, $\Gamma_p$ will be the set of substitution into closed reducible terms, and we will prove $t[\gamma] \in T_p$, a set of closed reducible term of type $T$ when $\gamma \in \Gamma_p$.

### 2022-06-18 coq-example.tex
Adapt style guide.

\subsection{Type Safety for STLC}
We start with the very basic type safety proof of STLC, largely adapted from Software Foundation\cite{pierce2014software}, which is also one of the primal motivating example of this project.

Our emphasis here is that, we singled out some programming language features from STLC and prove the type safety for each feature separately, following the style of the examples in MTC\citep{delaware2013,forsta2020}. And we use a \textit{not-yet-formally-defined} \textbf{mix-in} feature to mix the semantic and properties of two programming language feature -- product and boolean -- with vanilla STLC. This way, we can say precisely, \textit{a programming language feature itself is a piece of data/inheritance judgement/inherited family}. Compared to MTC, our example uses small-step operational semantic by exploiting the extensible inductive type, and most of the proof is directly adapted from the one in Software Foundation, resulting a more accessible proof. 
% In related work, Coq/Metatheory a la carte/Tion embedding can be emphasized as a more "semantic approach" because they encode the meaning using a special design pattern (for example, open recursive inductive type for extension), compared to our more syntactic approach. Their advantage is the transferability of this technique accross different proof assistants, and their disadvantage is that their approach are less accessible and unfriendly to amateur Coq users -- which can be reflected from the distance of their approach and text-book Software Foundation proof.

@@

\subsection{Abstract Interpreters for Imp}
The second example is adapted and modified from the Familia\citep{zm2017}
-- contrary to our first example, we use big-step interpreter and fuel to indicate the operational semantic on an imperative language with side-effect, and we specify the abstract interpretation and prove its soundness, with some of postulation on both computation and property. Then we extend the language feature and we instantiate the postulation on computation for both concrete interpreters and abstract interpreters. Thanks to the compilation, we can directly run the resulting abstract interpreters.

>>>>

\subsection{Type Safety for STLC}
We start with the very basic type safety proof of STLC, largely adapted from Software Foundation~\cite{pierce2014software}, which is also one of the primal motivating example of this project.

Our emphasis here is that, we singled out some programming language features from STLC and prove the type safety for each feature separately, following the style of the examples in MTC~\cite{delaware2013,forsta2020}. And we use a \textit{not-yet-formally-defined} \textbf{mix-in} feature to mix the semantic and properties of two programming language feature---product and boolean---with vanilla STLC. This way, we can say precisely, \textit{a programming language feature itself is a piece of data/inheritance judgement/inherited family}. Compared to MTC, our example uses small-step operational semantic by exploiting the extensible inductive type, and most of the proof is directly adapted from the one in Software Foundation, resulting a more accessible proof. 
% In related work, Coq/Metatheory a la carte/Tion embedding can be emphasized as a more "semantic approach" because they encode the meaning using a special design pattern (for example, open recursive inductive type for extension), compared to our more syntactic approach. Their advantage is the transferability of this technique accross different proof assistants, and their disadvantage is that their approach are less accessible and unfriendly to amateur Coq users---which can be reflected from the distance of their approach and text-book Software Foundation proof.

@@

\subsection{Abstract Interpreters for \texttt{Imp}}
The second example is adapted and modified from \citet{zm2017}
--- contrary to our first example, we use big-step interpreter and fuel to indicate the operational semantic on an imperative language with side-effect, and we specify the abstract interpretation and prove its soundness, with some of postulation on both computation and property. Then we extend the language feature and we instantiate the postulation on computation for both concrete interpreters and abstract interpreters. Thanks to the compilation, we can directly run the resulting abstract interpreters.

### 2022-06-18 coqimpl.tex
Adapt style guide.

Despite of the possible difficulty of the future maintenance, this approach has various advantages: 1. it is the easiest and the most accessible way to prototype as it relieves us the necessity of familarity of Coq base, especially for the implementation of the module and functor; 2. we have a clear definition of trusted-base -- the whole Coq; 3. it is easy to debug -- we just need to check the translated commands; 4. it can be well-incorporated with the existent tools like VSCoq; 5. it is more accessible for the the interested audience who can then easily adapt our plugin and give a try -- otherwise they have to download and re-build the whole customized Coq; 6. it is more stable because the surface syntax of Coq should be stable across different versions; 7. still, this plugin can capture the key ingredients of implementing family polymorphism inside Coq and act as a reference for guiding an appropriate implementation of Family Polymorphism inside all sorts of proof assistants.

\textbf{Family compiled into module.} This is the main idea of compiling family components into Coq's primitives: we compile family into coq module, family type into module type and context of a given term into parameters of the module. To achieve incremental type checking, we notice the nature of late binding: for each defining field $ .. \cL\sigma \vdash t : T $, we can compile $t$ using ``universal-quantifier-wrapped term'' : $.. \vdash \lambda t : \forall \cL \sigma. T$. However, instead of using Coq's universal quantifier, we use module and module parameters to achieve this wrapping -- each family type in the context of the judgement will be one module parameter with the compiled module type, and thus each field of the family will compile into a parametrized module (functor). Doing so we can also get rapid feedback from type checking when the users are defining each field interactively with Coq.
% Insert one pseudo-code example for explanation of the mechanism
\begin{figure}
  \begin{minipage}[t]{0.25\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Family A.
Field a : nat 
  := 1.
Field b 
  : self_A.a = self_A.a
  := eq_refl.
EndFamily.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.4\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module a_4 (self_A: EmptySig).
Definition a : nat := 1. End a_4.
Module Type a_5 (self_A: EmptySig).
Parameter (a : nat). End a_5.
Module Type a_6 := a_5 EmptyMod.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.3\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module b_7 (self_A: a_6).
Definition b 
  : self_A.a = self_A.a 
  := eq_refl. End b_7.

@@

% Concrete details of compilation of a family term data structure
Taking Figure \ref*{fig:plugin-example1} as an example: when the user interactively input the line "Field a : nat := ..", our plugin will translate this statement into the "Module a_9", "Module Type a_10, a_11" three components. {The "EmptySig" is just empty module type.} Then, these modules and module types will be generated and type-checked by Coq immediately. The computed "Module a_10" is then part of the context of "Field b" (as the module type of "self__A") for "b" to refer to. The internal representation of family "A" is simply the list of these ``compiled'' modules and module types. We can simply achieve incremental checking and overriding -- for example, we want to override "Field a", we simply replace that compiled module with the new module inside the list.

Now that we know a family data structure is actually a list of compiled modules, we may want to aggregate them into one complete compiled module. We achieve that by repeatedly using Coq's "Include" command as the example illustrated. Note that, in our example, we include two functors without arguments -- this is due to one of the feature of "Include": non-instantiated parameters will be automatically instantiated by the appropriate fields in the surrounding defining module. The resulting module is just like mundane Coq's module and thus enjoy all the computational mechanism from Coq for free.

@@

An inheritance data will be annotated with the type for the input family and output family, and generally there are three kinds of inheritance -- extend, override and inherit. Extending corresponds to adding new fields, overriding corresponds to modify existent fields and inheriting corresponds to directly taking fields from the parent. Thus it is possible to consider inheritance as solely a data rather than a functor, and this actually provides us the ability to \text{mix-in} inheritance data.

\textbf{Reasoning Requires Non-Overridable.}
Unlike general-purposed programming, Coq should be able to  \textit{reason} about each program. However, sometimes reasoning requires a specific program and overriding on them is unacceptable. For example, we may define a field $"add" : \mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ as one field and intends to proving its commutativity in a following field $"comm"$. But to prove so, we need to know more than just a type interface of $"add"$ but also its \textbf{concrete definition}. Otherwise, in the future, once $"add"$ is overridden into a subtraction function then $"comm"$ will have problem to be  inherited. A more concrete example is in Figure \ref*{fig:plugin-example1}, consider we have "Field b : self_A.a = 1 := .." instead, then our compilation and Coq's type check will both fail: in the context of "b" (module type "a_6") we only know "a" is of type nat but nothing more.  To fix that, we need more information on "a" than its type -- we need to expose its concrete definition "a = 1" to appear in the context of "b".

@@

To resolve this, we provide family sealing mechanism -- basically we allow the users to specify the family/module type, and thus we can have a ``local'' transparent, non-overridable field located in a overridable family. Using the above example, we simply make \mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an overridable family, but "f" to be non-overridable and transparent on its definition, and thus we can prove "p". Once we want to swap the implementation, we just override the whole ``sealed'' family.

This ``sealed'' family actually simulate interface to a certain level -- we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}  , and later instantiate them with concrete implementation by overriding this family.
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

\textbf{Special Fields: ``Extensible'' Inductive Type and Defining Recursor.}
We don't actually support extensible inductive type in Coq (because that require non-trivial research effort on theory side -- i.e. {What is the semantic of extensible inductive type?} -- and engineering), but we simulate extensible inductive type using overriding -- when extending an inductive type $A$ with new constructors $c$, our plugin will generate a new inductive definition $A'$ with this new $c$ on the fly and feed to Coq.  But still, we must be careful on the exposing data in the family type (module type) for the following field.

@@

To construct a recursor, we make for each constructor a handler and aggregate them inside a family. The whole family "neg_handler" can be considered as a large matching case. Doing so, family inheritance can function as matching-case reuse. Then we use "FRecursor" to specify the motive and inductive type. Here "FRecursor" will feed Coq
a module "v_33_34" for doing type-checking -- what it does is basically assert the existence of the recursor and apply to see if handlers can pass the type checking by Coq.

Since the recursor is constructed knowing a concrete inductive type, thus not inheritable, for all the children, we have to reconstruct and override with a new recursor (acting like an extra exhaustiveness checking). This is affordable since each recursor handler doesn't need to be rechecked -- look at "B2.neg_handler", there is only one new handler for "uu" and the handlers from the parent "B.neg_handler.tt,B.neg_handler.ff" are already type-checked and inherited(thanks to the fact that they only rely on ``the abstracted interface'' module "b_3"). Of course, our plugin will ``inherits'' the recursor "neg" but what the plugin does is doing exhaustiveness checking, again.

@@

\textbf{Propositional Partial Recursor.}
Apparently, the exposed module "b_3" in \cref*{fig:plugin-example2} is not expressive enough. For example, we cannot prove the constructors are injective, i.e. \mintinline{Coq}{self_B.tt ≠ self_B.ff}. In the original setting, to prove injectiveness of constructor we only require a recursor and its computational rules. However, as we pointed out earlier, the recursor of an inductive type cannot be exposed into the context for the sake of extensibility. We may have to alter the formulation of the recursor.

The simplest idea is to allow partiality -- i.e. returning \mintinline{Coq}{option T} instead of the original \mintinline{Coq}{T}. We call this \textit{propositional partial recursor}. For example, the propositional partial recursor for \mintinline{Coq}{B.b} is 
\begin{minted}{Coq}
b_prec : forall P : b -> Set, P tt -> P ff 
    -> forall x : b, option (P x). 
\end{minted}
with appropriate computational axioms. The partiality doesn't break extensibility (i.e. all the future extension of "b" can support this "b_prec").

@@

This style of ``Global Reasoning'' is that we can only prove the corresponding theorem when we know the ``full pictures'', including the inductive type. We provide "Closing Fact" as a command to carry out this global reasoning -- we can attach "Closing Fact" with either (proof) terms or Coq's proof script, then only when compilation to module happens, the term/proof script will put into type-check to see if a "Closing Fact" statement can be proved. Note that, "Closing Fact" cannot immeidately check the correctness of the term/proof script because this verification only happens when we finished defining a family, and thus not easy to handle.

This "Closing Fact" can ease us from the necessity to let plugin generate proof for recursors and partial recursors, and thus making plugin development easier. For example, the computation rule for a concrete recursor like "B.neg" and partial recursors in \cref*{fig:plugin-example2} can be directly asserted by using "Closing Fact" and verified later during compilation. This ``Global Reasoning'' will be again useful in the later examples.

>>>>

Despite of the possible difficulty of the future maintenance, this approach has various advantages: 1. it is the easiest and the most accessible way to prototype as it relieves us the necessity of familarity of Coq base, especially for the implementation of the module and functor; 2. we have a clear definition of trusted-base---the whole Coq; 3. it is easy to debug---we just need to check the translated commands; 4. it can be well-incorporated with the existent tools like VSCoq; 5. it is more accessible for the the interested audience who can then easily adapt our plugin and give a try---otherwise they have to download and re-build the whole customized Coq; 6. it is more stable because the surface syntax of Coq should be stable across different versions; 7. still, this plugin can capture the key ingredients of implementing family polymorphism inside Coq and act as a reference for guiding an appropriate implementation of Family Polymorphism inside all sorts of proof assistants.

\textbf{Family compiled into module.} This is the main idea of compiling family components into Coq's primitives: we compile family into coq module, family type into module type and context of a given term into parameters of the module. To achieve incremental type checking, we notice the nature of late binding: for each defining field $ .. \cL\sigma \vdash t : T $, we can compile $t$ using ``universal-quantifier-wrapped term'' : $.. \vdash \lambda t : \forall \cL \sigma. T$. However, instead of using Coq's universal quantifier, we use module and module parameters to achieve this wrapping---each family type in the context of the judgement will be one module parameter with the compiled module type, and thus each field of the family will compile into a parametrized module (functor). Doing so we can also get rapid feedback from type checking when the users are defining each field interactively with Coq.
% Insert one pseudo-code example for explanation of the mechanism
\begin{figure}
  \begin{minipage}[t]{0.25\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Family A.
Field a : nat 
  := 1.
Field b 
  : self_A.a = self_A.a
  := eq_refl.
EndFamily.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.4\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module a_4 (self_A: EmptySig).
Definition a : nat := 1. End a_4.
Module Type a_5 (self_A: EmptySig).
Parameter (a : nat). End a_5.
Module Type a_6 := a_5 EmptyMod.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.3\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module b_7 (self_A: a_6).
Definition b 
  : self_A.a = self_A.a 
  := eq_refl. End b_7.

@@

% Concrete details of compilation of a family term data structure
Taking \cref{fig:plugin-example1} as an example: when the user interactively input the line "Field a : nat := ..", our plugin will translate this statement into the "Module a_9", "Module Type a_10, a_11" three components. {The "EmptySig" is just empty module type.} Then, these modules and module types will be generated and type-checked by Coq immediately. The computed "Module a_10" is then part of the context of "Field b" (as the module type of "self__A") for "b" to refer to. The internal representation of family "A" is simply the list of these ``compiled'' modules and module types. We can simply achieve incremental checking and overriding---for example, we want to override "Field a", we simply replace that compiled module with the new module inside the list.

Now that we know a family data structure is actually a list of compiled modules, we may want to aggregate them into one complete compiled module. We achieve that by repeatedly using Coq's "Include" command as the example illustrated. Note that, in our example, we include two functors without arguments---this is due to one of the feature of "Include": non-instantiated parameters will be automatically instantiated by the appropriate fields in the surrounding defining module. The resulting module is just like mundane Coq's module and thus enjoy all the computational mechanism from Coq for free.

@@

An inheritance data will be annotated with the type for the input family and output family, and generally there are three kinds of inheritance---extend, override and inherit. Extending corresponds to adding new fields, overriding corresponds to modify existent fields and inheriting corresponds to directly taking fields from the parent. Thus it is possible to consider inheritance as solely a data rather than a functor, and this actually provides us the ability to \text{mix-in} inheritance data.

\textbf{Reasoning Requires Non-Overridable.}
Unlike general-purposed programming, Coq should be able to  \textit{reason} about each program. However, sometimes reasoning requires a specific program and overriding on them is unacceptable. For example, we may define a field $"add" : \mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ as one field and intends to proving its commutativity in a following field $"comm"$. But to prove so, we need to know more than just a type interface of $"add"$ but also its \textbf{concrete definition}. Otherwise, in the future, once $"add"$ is overridden into a subtraction function then $"comm"$ will have problem to be  inherited. A more concrete example is in \cref{fig:plugin-example1}, consider we have "Field b : self_A.a = 1 := .." instead, then our compilation and Coq's type check will both fail: in the context of "b" (module type "a_6") we only know "a" is of type nat but nothing more.  To fix that, we need more information on "a" than its type---we need to expose its concrete definition "a = 1" to appear in the context of "b".

@@

To resolve this, we provide family sealing mechanism---basically we allow the users to specify the family/module type, and thus we can have a ``local'' transparent, non-overridable field located in a overridable family. Using the above example, we simply make \mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an overridable family, but "f" to be non-overridable and transparent on its definition, and thus we can prove "p". Once we want to swap the implementation, we just override the whole ``sealed'' family.

This ``sealed'' family actually simulate interface to a certain level---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}  , and later instantiate them with concrete implementation by overriding this family.
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

\textbf{Special Fields: ``Extensible'' Inductive Type and Defining Recursor.}
We don't actually support extensible inductive type in Coq (because that require non-trivial research effort on theory side---i.e. {What is the semantic of extensible inductive type?}---and engineering), but we simulate extensible inductive type using overriding---when extending an inductive type $A$ with new constructors $c$, our plugin will generate a new inductive definition $A'$ with this new $c$ on the fly and feed to Coq.  But still, we must be careful on the exposing data in the family type (module type) for the following field.

@@

To construct a recursor, we make for each constructor a handler and aggregate them inside a family. The whole family "neg_handler" can be considered as a large matching case. Doing so, family inheritance can function as matching-case reuse. Then we use "FRecursor" to specify the motive and inductive type. Here "FRecursor" will feed Coq
a module "v_33_34" for doing type-checking---what it does is basically assert the existence of the recursor and apply to see if handlers can pass the type checking by Coq.

Since the recursor is constructed knowing a concrete inductive type, thus not inheritable, for all the children, we have to reconstruct and override with a new recursor (acting like an extra exhaustiveness checking). This is affordable since each recursor handler doesn't need to be rechecked---look at "B2.neg_handler", there is only one new handler for "uu" and the handlers from the parent "B.neg_handler.tt,B.neg_handler.ff" are already type-checked and inherited(thanks to the fact that they only rely on ``the abstracted interface'' module "b_3"). Of course, our plugin will ``inherits'' the recursor "neg" but what the plugin does is doing exhaustiveness checking, again.

@@

\textbf{Propositional Partial Recursor.}
Apparently, the exposed module "b_3" in \cref{fig:plugin-example2} is not expressive enough. For example, we cannot prove the constructors are injective, i.e. \mintinline{Coq}{self_B.tt ≠ self_B.ff}. In the original setting, to prove injectiveness of constructor we only require a recursor and its computational rules. However, as we pointed out earlier, the recursor of an inductive type cannot be exposed into the context for the sake of extensibility. We may have to alter the formulation of the recursor.

The simplest idea is to allow partiality---i.e. returning \mintinline{Coq}{option T} instead of the original \mintinline{Coq}{T}. We call this \textit{propositional partial recursor}. For example, the propositional partial recursor for \mintinline{Coq}{B.b} is 
\begin{minted}{Coq}
b_prec : forall P : b -> Set, P tt -> P ff 
    -> forall x : b, option (P x). 
\end{minted}
with appropriate computational axioms. The partiality doesn't break extensibility (i.e. all the future extension of "b" can support this "b_prec").

@@

This style of ``Global Reasoning'' is that we can only prove the corresponding theorem when we know the ``full pictures'', including the inductive type. We provide "Closing Fact" as a command to carry out this global reasoning---we can attach "Closing Fact" with either (proof) terms or Coq's proof script, then only when compilation to module happens, the term/proof script will put into type-check to see if a "Closing Fact" statement can be proved. Note that, "Closing Fact" cannot immeidately check the correctness of the term/proof script because this verification only happens when we finished defining a family, and thus not easy to handle.

This "Closing Fact" can ease us from the necessity to let plugin generate proof for recursors and partial recursors, and thus making plugin development easier. For example, the computation rule for a concrete recursor like "B.neg" and partial recursors in \cref{fig:plugin-example2} can be directly asserted by using "Closing Fact" and verified later during compilation. This ``Global Reasoning'' will be again useful in the later examples.

### 2022-06-18 metatheory.tex
Swap section meta-theory and impl. Please check Thm 3.1, justify that partial recursor is good enough.
Adapt style guide.

We start with the formulation of the syntax, which is based on the formalization of a predicative \textit{Martin-Lof Type Theory} (MLTT) given by \citep{coquand2018canonicity}. Thus we will omit a great deal of details about MLTT here but focus on the new facility we introduced.

Though phrased in Latex, we are following \citet{altkap2016} to use as
our meta-logic a type theoretical framework (like Agda), 
together with \textit{Quotient Inductive Inductive Type} (QIIT). Each
judgement will actually be represented by a QIIT type, which are
mutually recursively defined together. Quotient is used to represent
judgemental(definitional) equality, thanks to which we can have a
concise representation. This way, for all four kinds of judgement we are
using, there are always equality among these data. Doing so, we can omit
some obvious equality judgement. Most of the reasoning can be formulated
using the \textit{algebra} of QIIT (mapping out function from this
quotient data-type).

@@

\newcommand{\denotes}[1]{{\llbracket {#1} \rrbracket}}
\newcommand{\denotesS}[1]{{{\llbracket {#1} \rrbracket}_S}}
\newcommand{\goodCtx}[2]{{ {#1} \ \vdash }}
\newcommand{\goodType}[3]{{ {#1} \vdash {#2} }}
\newcommand{\goodTerm}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSub}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSig}[3]{{ {#1} \vdash {#2} \ \  Sig^{#3} }}
\newcommand{\goodWSig}[3]{{ {#1} \vdash {#2} \ \ WSig^{#3} }}
\newcommand{\goodSeal}[4]{{ {#1} \vdash {#2} : {#3} \  |\  {#4} }}
\newcommand{\goodInh}[4]{{ {#1} \vdash {#2} : {#3} \twoheadrightarrow {#4}}}
\newcommand{\nat}{\mathbf{N}}

\newcommand{\cU}{{\mathcal{U}}}
\newcommand{\cB}{{\mathbb{B}}}
\newcommand{\cL}{{\mathcal{L}}}
\newcommand{\cC}{{\mathcal{C}}}
\newcommand{\cCt}{{\mathcal{C}_t}}
\newcommand{\bW}{{\mathbb{W}}}

>>>>

We start with the formulation of the syntax, which is based on the formalization of a predicative \textit{Martin-Lof Type Theory} (MLTT) given by~\citet{coquand2018canonicity}. Thus we will omit a great deal of details about MLTT here but focus on the new facility we introduced.

Though phrased in Latex, we are following~\citet{altkap2016} to use as
our meta-logic a type theoretical framework (like Agda), 
together with \textit{Quotient Inductive Inductive Type} (QIIT). Each
judgement will actually be represented by a QIIT type, which are
mutually recursively defined together. Quotient is used to represent
judgemental(definitional) equality, thanks to which we can have a
concise representation. This way, for all four kinds of judgement we are
using, there are always equality among these data. Doing so, we can omit
some obvious equality judgement. Most of the reasoning can be formulated
using the \textit{algebra} of QIIT (mapping out function from this
quotient data-type).

@@
